Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-16 Draft/crosssectionLO.tex
Add BONSAY integrated cross sections

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X$ & $0.0002$ \\
        {\sc MG5\_aMC}&  $1.435$ & $0.004$ TO BE UPDATED  \\
        {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\
        {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
        {\sc Powheg-Box}  &  $1.44092$ & $0.00009$ \\
        {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
        {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $
    \end{tabular}
    \caption{\label{tab:wg1_LOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
    The uncertainties shown refers to the estimated statistical error of the Monte Carlo programs.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
    \MP{Please add or check your respective numbers}}
\end{table}

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline
        \hline
        {\sc Bonsay}  &  $1.43636 \pm 0.00002$ \\
        {\sc MG5\_aMC}&  $1.435$ & $0.004$ TO BE UPDATED  \\
        {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\
        {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
        {\sc Powheg-Box}  &  $1.44092$ & $0.00009$ \\
        {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
        {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $
    \end{tabular}
    \caption{\label{tab:wg1_LOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
    The uncertainties shown refers to the estimated statistical error of the Monte Carlo programs.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
    \MP{Please add or check your respective numbers}}
\end{table}

### 2018-02-16 Draft/crosssectionNLO.tex
Add BONSAY integrated cross sections

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X$ & $0.0009$  \\
        {\sc MG5\_aMC}&  $1.363\phantom{0}$ & $0.004$  \\
        {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
        {\sc Powheg-Box}  &  $1.362$   $0.003$   \\
        {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha^6)$.
    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
    \MP{Please add or check your respective numbers.}}
    \MR{My $t$-/$u$-channel-only number is $1.3703(1)$, so something additionally must be going on with Powheg, which we should comment on.}
    \AK{The number here was wrong. I have updated the table and plots. I am also running some more statistics... }
\end{table}

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline
        \hline
        {\sc Bonsay}  &  $1.35039 \pm 0.00006$  \\
        {\sc MG5\_aMC}&  $1.363\phantom{0}$ & $0.004$  \\
        {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
        {\sc Powheg-Box}  &  $1.362$  & $0.003$   \\
        {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha^6)$.
    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
    \MP{Please add or check your respective numbers.}}
    \MR{My $t$-/$u$-channel-only number is $1.3703(1)$, so something additionally must be going on with Powheg, which we should comment on.}
    \AK{The number here was wrong. I have updated the table and plots. I am also running some more statistics... }
\end{table}
